Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-08 paper/paper.tex
update table

\centerline{\begin{tikzpicture}[]
    \scriptsize
    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
    % set and set sampler
    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
    \node[below of=1] at (SN) {Set};
    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
    \def\dx{-3};
    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
    \node at (\dx, -1.2) {$\ldots$};
    \node[above of=2] at (T) (textT) {Tropical};
    \draw[black,-latex] (textT) -- (T);
\end{tikzpicture}}
\vspace{2em}
\centering{
\begin{minipage}{0.8\columnwidth}\scriptsize
\begin{tabularx}{\textwidth}{bb}
    \textbf{element type}     & \textbf{property to compute} \\
    {$\mathbbm{R}$}     & {the number of independent sets} \\
    {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
\end{tabularx}
\end{minipage}
}

>>>>

\centerline{\begin{tikzpicture}[]
    \scriptsize
    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
    % set and set sampler
    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
    \node[below of=1] at (SN) {Set};
    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
    \def\dx{-3};
    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
    \node at (\dx, -1.2) {$\ldots$};
    \node[above of=2] at (T) (textT) {Tropical};
    \draw[black,-latex] (textT) -- (T);
\end{tikzpicture}}
\vspace{2em}
\centering{
\begin{minipage}{0.8\columnwidth}\scriptsize
\begin{tabularx}{\textwidth}{bb}
    \textbf{element type}     & \textbf{property to compute} \\
    {$\mathbbm{R}$}     & {the number of independent sets} \\
    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
\end{tabularx}
\end{minipage}
}
